Spring haul-out behavior of seals in the Bering and Chukchi seas

### 2024-05-29 analysis/paper/London_HauloutBehavior.Rmd
rename figures to Figure-##

>>>>

make_plot_namer <- function(prefix="Figure-", fig_n=1L, width=2){
  function(x){
    x2 <- file.path(dirname(x), 
                    paste0(prefix, 
                           formatC(fig_n, width=width, flag="0"),
                           ".", 
                           tools::file_ext(x)))
    fig_n <<- fig_n + 1L
    if (file.rename(x, x2)) x2 else x
  }
}

knitr::opts_chunk$set(fig.process = make_plot_namer(width=3))
